A holomorphic approach to membranes and fivebranes

### 2022-06-15 fivebranes/twisted.tex
boundary

%\documentclass[11pt]{amsart}%

%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}

%\begin{document}

@@

  \item Deform the theory on the complement of the zero section by a certain maurer-cartan element. The Maurer-Cartan element is thought of as the flux sourced by branes wrapping the zero section.

  \item The complement of the zero section is a manifold with boundary - we impose a natural boundary condition.

@@

\parsec

As above, let $Z$ be a three-fold, $V\to Z$ a rank 2 holomorphic vector bundle such that $\wedge^{2} V \cong K_{Z}$, and let $X = {\rm Tot}V$. The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold - in the main body of the paper we will restrict ourselves to $V = K_{Z}^{1/2}\otimes \C^{2}$. We will view $\R\times X = {\rm Tot}(\R\oplus V)$, and consider a stack of N fivebranes wrapping the zero section in $\R\oplus V$.

We begin by describing the complement of the zero section
\[
M = \R\oplus V \setminus 0\times Z.
\]

Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation - the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \bar T_{Z}$. Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$. Explicitly, the corresponding norm is given by
\begin{align*}
 \pi:  \R\times X & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. Let $V_{M}$ denote the vertical tangent bundle to $(\pi, p)$, which we view as a subbundle of the real tangent bundle $T_{M}$. The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure. Indeed, letting $\iota : M \to \R\times X$ denote the standard inclusion, we may consider the pair
\[
  V_{M}\cap \iota^{*} T_{\R}, \ \ \ \ \ V\cap \iota^{*} T_{Z}.
\]

@@

We wish to describe the pushforward $(\pi, p)_{*}\cL_{sugra}$. The underlying sheaf of cochain complexes is given by

>>>>

\documentclass[11pt]{amsart}%

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}
\newcommand{\thfd}{\Bar{D}}
\newcommand{\thfdel}{D}

\begin{document}

@@

  \item Deform the theory on the complement of the zero section by a certain Maurer--Cartan element. 
  The Maurer--Cartan element is thought of as the flux sourced by branes wrapping the zero section.

  \item The complement of the zero section is a manifold with boundary---we impose a natural boundary condition.

@@

\parsec[s:brfive]

We first consider the situation of backreacting some number of (twisted) fivebrans.
Let $Z$ be a three-fold that the fivebranes wrap. 
Let $V\to Z$ a rank 2 holomorphic vector bundle such that $\wedge^{2} V \cong K_{Z}$, and let $X = \text{Tot}(V)$. 
The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold---in the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$. 
The eleven-manifold we place our theory on is $\R\times X_V$, which we can view as the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.

We place a stack of $N$ fivebranes wrapping the zero section in $\R\oplus V$.
Denote the complement of the zero section by
\[
M_V = \text{Tot}(\R\oplus V) - 0(Z).
\]
Notice that in \S \ref{s:Lsugra} we have only defined the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on a product of a smooth one-manifold times a Calabi--Yau five-fold.
The eleven-manifold $M_V$ is not of this form, nevertheless there is a generalization of $\cL_{sugra}$ which one can define using the natural geometric structure present in our situation.

A transversely holomorphic foliation (THF) on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$. 
We will say that $F$ equips $M$ with the a THF structure. 
%Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
The product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $N$ along the projection. 
Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
The bundle $F$ is locally spanned by the vector fields $\partial / \partial x_i$'s and $\del/\del \zbar_j$'s. 
(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)

Any submanifold of a THF manifold is itself a THF manifold. 
We are most interested in the submanifold $M_V \subset {\rm Tot}(\R \oplus V) = \R \times X$ where we equip $\R \times X$ with its standard split THF structure.

We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology. 
Let us focus on the fields $\beta,\gamma$ which on $\R \times X$ combine to form the complex 
\beqn\label{eqn:drdol}
\Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(\R) \otimes \Omega^{1,\bu}(X) .
\eeqn
As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
More generally, there is a natural cohomology associated to a THF structure.
Suppose $(M,F)$ is a THF structure and 
denote by $Q$ the (complex) quotient bundle $\T_\C M / F$.
For each $p,q$ denote by $\cA^{p;q}$ smooth sections of the bundle $\wedge^p Q^\vee \otimes \wedge^q F^\vee$. 
The derivative along the leaves of the foliation defined by $V$ defines a map 
\[
\thfd \colon \cA^{p;q} \to \cA^{p;q+1}  .
\]
By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and so $\thfd$ equips $\cA^{p;\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$. 
Locally in a split THF structure the operator $D$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$. 
There is also an analog of the holomorphic $\del$ operator which takes the form $\thfdel \colon \cA^{p;q} \to \cA^{p+1;q}$. 
The obvious exterior product $\cA^{p;q} \times \cA^{r;s} \to \cA^{p+r;q+s}$ further endows 
\[
\left(\cA^{\bu;\bu} (M), \thfd + \thfdel\right) = \left(\oplus_p \cA^{p;\bu}[-p] , \thfd + \thfdel \right) 
\]
with the structure of a bigraded commutative dg algebra.
This complex is simply isomorphic to the de Rham complex of $M$, but this presentation lends itself to more interesting quotient complexes. 
For example, the forms of type $(p,\bu)$ with $p \geq 2$ form an ideal inside of this dg algebra; hence we get a quotient dg algebra 
\beqn\label{thfcoh1}
\left(\cA^{\leq 1;\bu}(M), \thfd + \thfdel\right) = \quad \cA^{0;\bu} \xto{\thfdel} \cA^{1;\bu} .
\eeqn
We leave the $\thfd$ operator implicit in the presentation on the right hand side.
When $M = M_V$, it is this complex that is the THF generalization of the truncated de Rham--Dolbeault complex in \eqref{eqn:drdol}---it is easy to see that it agrees with this complex in the case of a split THF manifold.
There is a similar THF description for the fields $\mu,\nu$ in the eleven-dimensional theory.

%Note that the eleven-manifold $\R \times X$ is equipped with a natural transverseley--holomorphic foliation (THF)---the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \Bar{T}_{Z}$.
With this THF cohomological description of the eleven-dimensional theory in place we proceed to describe the boundary condition obtained by removing the location of the branes. 
We may choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus V$ over $Z$ and a fiberwise partially hermitian metric. 
Explicitly, the corresponding norm defines a map
\begin{align*}
 h \colon  \R\times X & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $\pi \colon \R\times X \to Z$ be the natural projection, we obtain the $S^{4}$ bundle 
\[
p \define (h,\pi) \colon \R \times X \to \R_{+}\times Z 
\] 
which restricts to an $S^4$ bundle $p|M \colon M \to \R_{>0} \times Z$.
These embeddings and projections fit inside of the following commutative diagram
\[
\begin{tikzcd} 
M \ar[d,"p|M"'] \ar[r,hook] & \R \times X \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
\R_{>0} \times Z \ar[r,hook] & \R_{+} \times Z & \ar[l,hook',"0 \times \id"] Z.
\end{tikzcd}
\]
The inclusions on the left are the natural embeddings. 
The top right inclusion is the zero section of ${\rm Tot}(\R \oplus V) = \R \times X$ and the bottom right inclusion is the embedding at radius $r = 0$.

As we just elaborated, the eleven-dimensional theory is defined on the THF manifold $M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $M$. 
Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|M$.
The resulting sheaf of $L_\infty$ algebras $(p|M)_*\cL_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.

The theory on $M$ extends to a theory on the manifold obtained by filling in the zero section of $\R \times V$; in other words, we know that the theory is defined on the entire space $\R \times X$.
This means that there is a natural way to extend the theory on $\R_{>0} \times Z$ to the seven-manifold with boundary $\R_{+} \times Z$. 
The restriction of this theory to the six-dimensional boundary plays the most important role for us.

\brian{trying to incorporate below}
%To do this we will make use of the natural foliated geometric structures which we have around.

Let $V_{M}$ denote the vertical tangent bundle to $(h, \pi)$, which we view as a subbundle of the real tangent bundle $T_{M}$. 
The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure. Indeed, if $\iota \colon M \to \R\times X$ is inclusion, then we consider the pair
\[
  V_{M}\cap \iota^{*} T_{\R}, \ \ \ \ \ V\cap \iota^{*} T_{Z}.
\]

@@

 The underlying sheaf of cochain complexes is given by
